\section{Core principles}


\subsection{sel4 microkernel}
"seL4 is a high-assurance, high-performance operating system microkernel. It is unique because of its comprehensive formal verification, without compromising performance." \cite{seL4:2024}

\subsection{Userspace}

\begin{itemize}
    \item Separation of concerns: Split the userspace into components that are well isolated from each other.
    \item Least priviledges: Grant each component only the priviledges it needs to full fill its tasks.    
    \item Fault tolerance: In userspace bugs may exist and and the idea is to recover from them while continuing to run.
    \item Live update: The system shall stay up, even in the face of major software updates.
\end{itemize}

\subsubsection{Least priviledges}

\subsubsection{Fault tolerance}
seL4 is proven to bug free. Contrary to this, the userspace services/servers aren't proven to be bug free. If such a service crashes, it is necessary to restart it automatically.
Minix3's reincanation server \cite{minix3:2010} implements the functionality to restart a crashed server. A similar concept is implemented to restart crashed services automatically to reach 
high availability.

\subsubsection{Live update}
Update without complete system restart.

\subsection{Rust}
Rust is a general-purpose programming language emphasizing performance, type safety, and concurrency. It enforces memory safety, meaning that all references point to valid memory[rust]. 
This is why it is predestined to be used as system programming language and used in this project.
